### 2017-03-12 README.Rmd
fixed pandoc conversion issues

---
output: 
  html_document: 
    keep_md: yes
---
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![Build Status](https://travis-ci.org/bgreenwell/pdp.svg?branch=master)](https://travis-ci.org/bgreenwell/pdp)
[![Coverage Status](https://img.shields.io/codecov/c/github/bgreenwell/pdp.svg)](https://codecov.io/github/bgreenwell/pdp?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/pdp)](http://cranlogs.r-pkg.org/badges/pdp)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)
[![Rdoc](http://www.rdocumentation.org/badges/version/pdp)](http://www.rdocumentation.org/packages/pdp)

>>>>

---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![Build Status](https://travis-ci.org/bgreenwell/pdp.svg?branch=master)](https://travis-ci.org/bgreenwell/pdp)
[![Coverage Status](https://img.shields.io/codecov/c/github/bgreenwell/pdp.svg)](https://codecov.io/github/bgreenwell/pdp?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/pdp)](http://cranlogs.r-pkg.org/badges/pdp)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)
[![Rdoc](http://www.rdocumentation.org/badges/version/pdp)](http://www.rdocumentation.org/packages/pdp)
